\input{preamble}

% OK, start here.
%
\begin{document}

\title{Introduction}


\maketitle

\phantomsection
\label{section-phantom}

\begin{verbatim}
Copyright (C) 2023 Camillo De Lellis
Permission is granted to copy, distribute and/or modify this
document under the terms of the GNU Free Documentation License,
Version 1.2 or any later version published by the Free Software
Foundation; with no Invariant Sections, no Front-Cover Texts,
and no Back-Cover Texts. A copy of the license is included in
the section entitled "GNU Free Documentation License".
\end{verbatim}

\tableofcontents


\section{Overview}
\label{section-overview}

\noindent
This is the first paragraph of the overview.
Why this project? Thanks to the stacks project.

\medskip\noindent
We expect this material to be read online as a key feature are the hyperlinks
giving quick access to internal references spread over many different pages.
If you use an embedded pdf or dvi viewer in your browser, the cross file
links should work.

\medskip\noindent
This project is a collaborative effort and we encourage you to help out.
Please email any typos or errors you find while reading or
any suggestions, additional material, or examples you have to
write an email to
\href{mailto:gmt-foundation@mailinator.com}{gmt-foundation@mailinator.com}.
You can download a tarball containing all source files, extract,
run make, and use a dvi or pdf viewer locally. Please feel free to
edit the LaTeX files and email your improvements.


\section{Attribution}
\label{section-attribution}

\noindent
The scope of this work is such that it is a daunting task to attribute
correctly and succinctly all of those mathematicians whose work has led
to the development of the theory we try to explain here. We hope eventually
to generate enough community interest to find contributors willing to write
sections with historical remarks for each and every chapter.

\medskip\noindent
Those who contributed to this work are listed on the title page of the book
version of this work and
\href{https://contabo3.matb.it/tex/CONTRIBUTORS}{online}.

\input{chapters}

\bibliography{my}
\bibliographystyle{amsalpha}

\end{document}
